Tampering Detection In Low-Power Smart Cameras

### 2015-05-29 paper.tex
Messe caption e diminuito size del pdf

\begin{figure}[t!]
\centering
\subfigure[]{\label{fig:pioggia} \includegraphics[width=0.4\linewidth]{Immagini/pioggia}}
\subfigure[]{\label{fig:neve} \includegraphics[width=0.4\linewidth]{Immagini/neve}}
\caption[Tampering examples]{Examples of tampering events due to atmospheric phenomena. \textbf{(a)} Blur due to rain drops on the camera lens. \textbf{(b)} Occlusion due to snow on the camera lens.}
\label{fig:tampering}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=1\linewidth]{Immagini/sequenze}
\caption{Sequences taken from webcams: \textbf{(a)} no tampering events; \textbf{(b)} defocus event on 4-th and 5-th frames, created using gaussian filtering; \textbf{(c)} displacement event on 4-th and 5-th frames, created using concatenation between similar sequences; \textbf{(d)} real displacement event on 4-th frame.}
\label{fig:sequences}
\end{figure}

@@

\begin{figure}[tb]
\centering
\includegraphics[width=1\linewidth]{Immagini/indicatori}
\caption{Example of displacement and behavior of the average value of the luma. The event comes at frame $157$ and the corresponding value of $l(t)$ is depicted with a red star. \textbf{(a)} Considering the average value of the luma in the whole scene. \textbf{(b)} and \textbf{(c)} Considering the average value of the luma in a specific region.}
\label{fig:indicatori} 
\end{figure}

@@

\section{Experiments}\label{sec:experiments}

Experiments are meant to show the effectiveness of the proposed algorithm on real-world sequences, and to specifically assess the advantage of using segmentation for detecting camera displacements. 
\subsubsection{Considered Methods}
As far as camera-displacement is concerned, Algorithm \eqref{alg:DISPL} is compared against three variants: 1) monitoring the luma on the whole image (\emph{Luma-Total}), 2) monitoring the total energy of the difference between two adjacent frames (\emph{Frame Difference}), and 3) monitoring the luma on $K$ regions obtained by clustering $[r(x), c(x)]$, which yields a Voronoi partitioning of the scene (\emph{Luma-Voronoi}). Frame difference is considered as a baseline technique for displacement detection, while comparison against \emph{Luma-Voronoi} shows the advantages of setting regions depending of the image content. In the experiments on blurring detection we compare Algorithm \ref{alg:DISPL} against monitoring the gradient separately over image regions, as done for $\partial l_k$.

\subsubsection{Datasets}
We acquired two datasets: the first dataset contains \gi{Adriano: how many?} sequences of \gi{Adriano: how many?} frames each that have been recorded from webcam monitoring urban areas (e.g., see Figure \ref{fig:sequences}(a)). The second dataset was recorded using a Raspberry Pi Model B+ \gi{Adriano: refrence} mounting a camera module. In the first dataset tampering was synthetically generated by blurring frames (see, Figure \ref{fig:sequences}(b)) or concatenating frames from different sequences depicting similar environments (see Figure \ref{fig:sequences}(c)). Few sequences of the first dataset contained real tampering events \gi{Adriano: quanti? solo displacement? niente blur considerato qui?} (Figure \ref{fig:indicatori}). In the second dataset, tampering was introduced by moving the device or spraying water on the camera lens. %\gi{una footnote dicendo sequences can be released upon request?}

\subsubsection{Performance Assessment}
The typical figure of merit for assessing detection performance in one-shot monitoring methods are the ROC curves: in our case, these can be computed by varying $\gamma_l$ and $\gamma_g$ in a range of values. In particular, each point in the ROC curve depicts a pair of values (1-SPECIFICITY, RECALL) defined as
\[1-\text{SPECIFICITY}_\gamma = \frac{\text{FP}_\gamma}{\text{TN}_\gamma+\text{FP}_\gamma}, \ \text{ and } \ \text{RECALL}_\gamma=\frac{\text{TP}_\gamma}{\text{TP}_\gamma+\text{FN}_\gamma}\]
where TP, FP, TN, FN represent the number of true positives (tampered frames correctly detected), of false positives (tampering-free frames detected), of true negatives (tampering-free frames not detected) and of false negatives (number of missed tampering frames), for a given value of threshold $\gamma_l$ (or $\gamma_g$).

\subsubsection{Discussion}
ROC curves and the AUC in Figure~\ref{fig:ROCdisplacement} caption indicate that camera displacements can be effectively detected. However, the best performance are achieved by Algorithm \ref{alg:DISPL} the (\emph{Frame-Difference} curve has not been reported because it was below these). This result indicate that separately monitoring the luma over image regions is an effective strategy and that the regions have to be carefully designed. Please note that, for the visualization sake, these ROC curves have been reported in a limited range of x and y axis. While the improvement might seem negligible we observe that Algorithm~\ref{alg:DISPL} achieves \gi{Adriano, quanto?} false positive rates (i.e., 1-SPECIFICITY) than..

>>>>

\begin{figure}[t!]
\centering
\subfigure[]{\label{fig:pioggia} \includegraphics[width=0.3\linewidth]{Immagini/pioggia}}
\subfigure[]{\label{fig:neve} \includegraphics[width=0.3\linewidth]{Immagini/neve}}
\caption[Tampering examples]{Examples of tampering events due to atmospheric phenomena. \textbf{(a)} Blur due to rain drops on the camera lens. \textbf{(b)} Occlusion due to snow on the camera lens.}
\label{fig:tampering}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.8\linewidth]{Immagini/sequenze}
\caption{Sequences taken from webcams: \textbf{(a)} no tampering events; \textbf{(b)} defocus event on 4-th and 5-th frames, created using gaussian filtering; \textbf{(c)} displacement event on 4-th and 5-th frames, created using concatenation between similar sequences.}
\label{fig:sequences}
\end{figure}

@@

\begin{figure}[tb]
\centering
\includegraphics[width=1\linewidth]{Immagini/indicatori}
\caption{Example of displacement. On the left side of the image is reported the behavior of the average value of the luma, while on the right side there is its detrending.
The event comes at frame $157$ and the corresponding value of $l(t)$ is depicted with a red star. 
\textbf{(a)} Considering the average value of the luma in the whole scene. 
\textbf{(b)} and \textbf{(c)} Considering the average value of the luma in a specific region.}
\label{fig:indicatori} 
\end{figure}

@@

\section{Experiments}\label{sec:experiments}
Experiments are meant to show the effectiveness of the proposed algorithm on real-world sequences, and to specifically assess the advantage of using segmentation for detecting camera displacements. 
\subsubsection{Considered Methods}
As far as camera-displacement is concerned, Algorithm \eqref{alg:DISPL} is compared against three variants: 1) monitoring the luma on the whole image (\emph{Luma-Total}), 2) monitoring the total energy of the difference between two adjacent frames (\emph{Frame Difference}), and 3) monitoring the luma on $K$ regions obtained by clustering $[r(x), c(x)]$, which yields a Voronoi partitioning of the scene (\emph{Luma-Voronoi}). Frame difference is considered as a baseline technique for displacement detection, while comparison against \emph{Luma-Voronoi} shows the advantages of setting regions depending of the image content. In the experiments on blurring detection we compare Algorithm \ref{alg:DISPL} against monitoring the gradient separately over image regions, as done for $\partial l_k$.
\subsubsection{Datasets}
We acquired two datasets: the first dataset contains \gi{Adriano: how many?} sequences of \gi{Adriano: how many?} frames each that have been recorded from webcam monitoring urban areas (e.g., see Figure \ref{fig:sequences}(a)). The second dataset was recorded using a Raspberry Pi Model B+ \gi{Adriano: refrence} mounting a camera module. In the first dataset tampering was synthetically generated by blurring frames (see, Figure \ref{fig:sequences}(b)) or concatenating frames from different sequences depicting similar environments (see Figure \ref{fig:sequences}(c)). Few sequences of the first dataset contained real tampering events \gi{Adriano: quanti? solo displacement? niente blur considerato qui?} (Figure \ref{fig:indicatori}). In the second dataset, tampering was introduced by moving the device or spraying water on the camera lens. %\gi{una footnote dicendo sequences can be released upon request?}
\subsubsection{Performance Assessment}
The typical figure of merit for assessing detection performance in one-shot monitoring methods are the ROC curves: in our case, these can be computed by varying $\gamma_l$ and $\gamma_g$ in a range of values. In particular, each point in the ROC curve depicts a pair of values (1-SPECIFICITY, RECALL) defined as
\[1-\text{SPECIFICITY}_\gamma = \frac{\text{FP}_\gamma}{\text{TN}_\gamma+\text{FP}_\gamma}, \ \text{ and } \ \text{RECALL}_\gamma=\frac{\text{TP}_\gamma}{\text{TP}_\gamma+\text{FN}_\gamma}\]
where TP, FP, TN, FN represent the number of true positives (tampered frames correctly detected), of false positives (tampering-free frames detected), of true negatives (tampering-free frames not detected) and of false negatives (number of missed tampering frames), for a given value of threshold $\gamma_l$ (or $\gamma_g$).
\subsubsection{Discussion}
ROC curves and the AUC in Figure~\ref{fig:ROCdisplacement} caption indicate that camera displacements can be effectively detected. However, the best performance are achieved by Algorithm \ref{alg:DISPL} the (\emph{Frame-Difference} curve has not been reported because it was below these). This result indicate that separately monitoring the luma over image regions is an effective strategy and that the regions have to be carefully designed. Please note that, for the visualization sake, these ROC curves have been reported in a limited range of x and y axis. While the improvement might seem negligible we observe that Algorithm~\ref{alg:DISPL} achieves \gi{Adriano, quanto?} false positive rates (i.e., 1-SPECIFICITY) than..
